---
title: "README-RMARKDOWN"
author: "Frank"
date: "2020/5/14"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lazy.work)
```

# lazy.work
Some R functions to save your time at Work

## Install

```r
devtools::install_github("frankzhangsyd/lazy.work")
```

## Main Usages

### Alteryx Related

**ayx_fl** : Convert a vector of column names and a function symbol`("+","-","*","/")` across all.

ie: 

```{r}
ayx_fl(c("a","b"))

```

**ayx_documentation** : Extract information of *Input*,*Output*,*Formula* tools in Alteryx and save to user pointed excel path. (have to end with `xlsx`)

ie: 

```{r, eval=FALSE}
ayx_documentation("Your/path/of/the/alteryx/workflow.yxmd",
                  "Your/path/of/the/output/excel/file.xlsx")

```


### Excel related

## Excel Columnn Names

**excel_column_letters**: A character vector contains all the column names (ie A,B,C,D) for excel.

```{r}
# First 5 columns
excel_column_letters[1:5]

```

```{r}
# Generate between two columns

excel_column_letters[which(excel_column_letters == "AE"):which(excel_column_letters == "AH")]
```


